---
title: "Parking infractions, City of Toronto take home assignment"
author: "Nima Jamshidi"
output: 
  html_notebook:
    toc: true
  pdf_notebook:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this notebook, I am going to study the most frequent parking infractions in Toronto with analyzing their locations and underlying factors. For this study, I'm using R programming language with the use of RStudio IDE. 

First step is to install and load the required packages.

```{r packages}
# suppressPackageStartupMessages(library(httr))
# suppressPackageStartupMessages(library(jsonlite))
#install.packages("opendatatoronto")
suppressPackageStartupMessages(library(opendatatoronto))
suppressPackageStartupMessages(library(ckanr))
#> Loading required package: DBI
suppressPackageStartupMessages(library(readr))
suppressPackageStartupMessages(library(vroom))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(sf))
suppressPackageStartupMessages(library(leaflet))
```

```{r parking ticket query 1}
PaTi_metadata <- opendatatoronto::show_package("https://open.toronto.ca/dataset/parking-tickets/")
PaTi_list <- opendatatoronto::list_package_resources("https://open.toronto.ca/dataset/parking-tickets/")
PaTi_data_tot <- tibble()
Col_type <- cols(
        tag_number_masked = col_character(),
        date_of_infraction = col_double(),
        infraction_code = col_double(),
        infraction_description = col_character(),
        set_fine_amount = col_double(),
        time_of_infraction = col_character(),
        location1 = col_character(),
        location2 = col_character(),
        location3 = col_character(),
        location4 = col_character(),
        province = col_character()
      )

# https://github.com/tidyverse/vroom/issues/138
Corrupted_csv <- function(dir,PaTi_data_id,save_path,Col_type) {
  resource_dir <- fs::dir_create(paste0(dir, "/", PaTi_data_id))
  csv_files <- unzip(save_path[["path"]], exdir = resource_dir)
  con <- file(csv_files, "rb")
  x <- readBin(con, "raw", n = 500000000)
  utf_text <- iconv(
        list(x),
        from = "UTF-16LE",
        to = "UTF-8",
        toRaw = F
      )
  res <-
    vroom::vroom(
      utf_text,
      delim = ",",
      col_types = Col_type,
      col_names = names(Col_type$cols),
      skip = 1
    ) %>% 
    mutate(time_of_infraction = replace_na(time_of_infraction, "0000"))
  return(res)
}

read_all_zip <- function(file, ...) {
  filenames <- unzip(file, list = TRUE)$Name
  vroom(purrr::map(filenames, ~ unz(file, .x)), ...)
}

PaTi_retrieve <- function(i){
  PaTi_data_id <- PaTi_list[[i,"id"]]
  resource <-
    resource_show(PaTi_data_id, url = "https://ckan0.cf.opendata.inter.prod-toronto.ca/", as = "list")
  dir <- tempdir()
  resource_dir <- fs::dir_create(paste0(dir, "/", PaTi_data_id))
  save_path <-
    ckan_fetch(
      resource[["url"]],
      store = "disk",
      path = paste0(dir, "/", PaTi_data_id, "/", "res.zip")
    )
  t <- try({
    # https://github.com/tidyverse/vroom/issues/125
    filenames <- unzip(save_path$path, list = TRUE)$Name
    res <- bind_rows(purrr::map(filenames, ~ vroom(unz(save_path$path, .x),
                                                   delim = ",",
                                                   col_names = names(Col_type$cols),
                                                   col_types = Col_type,
                                                   skip = 1)))
  })
  if (inherits(t, "try-error")|ncol(res)!=11)  {
    print("corrupted CSV")
    res <- Corrupted_csv(dir,PaTi_data_id,save_path,Col_type)}
  unlink(dir)
  return(res)
}

```

```{r parking ticket query 2, warning = FALSE}
for (i in str_which(PaTi_list$name, "parking-tickets-\\d")) {
  print(paste(str_extract(PaTi_list$name[i],"\\d+"),"started."))
  res <- PaTi_retrieve(i)
  print(paste(str_extract(PaTi_list$name[i],"\\d+"),"retrieval done!"))
  PaTi_data_tot <- PaTi_data_tot %>% rbind(res)
}
rm(Col_type,Pati_list,res,i,Corrupted_csv)
saveRDS(PaTi_data_tot,"PaTi_data_tot.rds")
PaTi_data_tot <- readRDS("PaTi_data_tot.rds") %>% filter(date_of_infraction>20200000)
```
```{r parking ticket explore}
Pati_rank <- PaTi_data_tot %>% 
  group_by(infraction_code, infraction_description) %>% 
  summarise(n = n()) %>% 
  mutate(n_tot = sum(n),
         infraction_description2 = infraction_description[which.max(nchar(infraction_description))],
         row_num = row_number()) %>% 
  filter(row_num == 1) %>% 
  select(-n, -infraction_description2,-row_num) %>% 
  arrange(desc(n_tot))
```

```{r geocoder}
GeoC_metadata <- opendatatoronto::show_package("https://open.toronto.ca/dataset/address-points-municipal-toronto-one-address-repository/")
GeoC_list <- opendatatoronto::list_package_resources("https://open.toronto.ca/dataset/address-points-municipal-toronto-one-address-repository/")
GeoC_retrieve <- function() {
  GeoC_data_id <- GeoC_list[[3, "id"]]
  resource <-
    resource_show(GeoC_data_id, url = "https://ckan0.cf.opendata.inter.prod-toronto.ca/", as = "list")
  dir <- tempdir()
  resource_dir <- fs::dir_create(paste0(dir, "/", GeoC_data_id))
  save_path <-
    ckan_fetch(
      resource[["url"]],
      store = "disk",
      path = paste0(dir, "/", GeoC_data_id, "/", "res.zip")
    )
  GeoC_files <- unzip(save_path[["path"]], exdir = resource_dir)
  GeoC_shp <- st_read(GeoC_files[str_ends(GeoC_files, ".shp")])
}

GeoC_shp <- GeoC_retrieve()
GeoC_shp <- GeoC_shp %>% mutate(LFNAME_lower = tolower(LFNAME))

```
```{r find point}
PaTi_data_top20_split <- PaTi_data_tot %>%
  filter(infraction_code %in% Pati_rank$infraction_code[1:20]) %>% 
  mutate(group = grepl('^[[:punct:]]?\\d', location2))

PaTi_data_top20_1 <-  PaTi_data_top20_split[PaTi_data_top20_split$group,] %>% 
  group_by(infraction_code,location2) %>% 
  summarise(n=n()) %>% 
  rowwise() %>%
  mutate(ADDRESS = str_extract(str_extract(location2,"^[:punct:]?\\d*((?<=\\d)[:alpha:](?=\\s))?"),"[^[:punct:]]+"),
         LFNAME_lower = tolower(str_trim(sub(ADDRESS,"",location2)))) %>% 
  left_join((GeoC_shp %>% select(GEO_ID,LINK,LFNAME_lower,ADDRESS)),by = c("LFNAME_lower","ADDRESS")) %>% 
  group_by(infraction_code, LINK) %>%
  summarise(n = sum(n,na.rm = TRUE)) %>% 
  mutate(accurate_type = T,
         reference_type = "LINK") %>% 
  rename(reference = LINK)

PaTi_data_top20_2 <- PaTi_data_top20_split[!PaTi_data_top20_split$group,] %>%  
  group_by(infraction_code,location2,location4) %>% 
  summarise(n=n()) %>% 
  rowwise() %>%
  mutate(location2 = tolower(str_trim(location2)),
         location4 = tolower(str_trim(location4))) 

Intersection_geocoder <- function(location2,location4){
  shp1 <- GeoC_shp %>% 
    filter(LFNAME_lower == location2)
  if (nrow(shp1)==0){return(NA)}
  shp1 <- shp1 %>% group_by(LINK) %>% 
    filter(DISTANCE %in% c(min(DISTANCE),max(DISTANCE)))
  
  shp2 <- GeoC_shp %>% 
    filter(LFNAME_lower == location4) 
  if (nrow(shp2)==0){return(NA)}
  shp2 <- shp2 %>% group_by(LINK) %>% 
    filter(DISTANCE %in% c(min(DISTANCE),max(DISTANCE)))
  
  dist = st_distance(shp1,shp2)
  ind = which(dist == min(dist), arr.ind = TRUE)
  location = shp1[ind[1],][["GEO_ID"]]
  return(location)
}

GeoC_shp_intersection <- PaTi_data_top20_2 %>% ungroup() %>% select(location2,location4) %>% distinct() %>% 
  mutate(GEO_ID = purrr::map2_dbl(location2,location2,Intersection_geocoder))

saveRDS(GeoC_shp_intersection,"GeoC_shp_intersection.rds")
GeoC_shp_intersection <- readRDS("GeoC_shp_intersection.rds")


PaTi_data_top20_2 <- PaTi_data_top20_2 %>% left_join(GeoC_shp_intersection,by = c("location2","location4")) %>% 
  group_by(infraction_code, GEO_ID) %>%
  summarise(n = sum(n,na.rm = TRUE)) %>% 
  mutate(accurate_type = F,
         reference_type = "GEO_ID") %>% 
  rename(reference = GEO_ID)

PaTi_data_top20 <- PaTi_data_top20_1 %>%
  rbind(PaTi_data_top20_2) %>% 
  filter(!is.na(reference)) %>% 
  group_by(infraction_code) %>%
  filter(n == max(n)) %>% 
  arrange(desc(n))
```

```{r Q1 plot}
PaTi_polygon_1 <- GeoC_shp %>% 
  inner_join((PaTi_data_top20 %>%
               filter(reference_type == "LINK") %>%
               select(infraction_code,reference,no_infraction = n)),
             by = c("LINK"="reference")) %>% 
  left_join((Pati_rank %>% select(starts_with("infraction"))),by = "infraction_code") %>% 
  group_by(infraction_code, no_infraction, infraction_description, LFNAME) %>% 
  summarise(n_link=n())

PaTi_polygon_2 <- GeoC_shp %>% 
  inner_join((PaTi_data_top20 %>%
               filter(reference_type == "GEO_ID") %>%
               select(infraction_code,reference,no_infraction = n)),
             by = c("GEO_ID"="reference")) %>% 
  left_join((Pati_rank %>% select(starts_with("infraction"))),by = "infraction_code") %>% 
  group_by(infraction_code, no_infraction, infraction_description, LFNAME) %>% 
  summarise(n_link=n())

PaTi_polygon_make <- function(data) {
  if (data$n_link[1] == 1) {
    data %>%
      # summarise(n_link = n()) %>%
      # filter(n_link == 1) %>%
      st_transform(3347) %>%
      st_buffer(dist = 10) %>%
      st_transform(4326) %>% 
      st_cast("POLYGON")
  } else if (data$n_link[1] == 2) {
    data %>%
      # summarise(n_link = n()) %>%
      st_cast("LINESTRING") %>%
      st_transform(3347) %>%
      st_buffer(dist = 10) %>%
      st_transform(4326)
  } else if (data$n_link[1] == 3) {
    temp = data %>% st_coordinates()
    st_geometry(data) = st_geometry(st_as_sf(as.data.frame(temp[c(1,1,2,3),]),coords = c("X","Y"),crs = st_crs(data)) %>% summarise())
    data %>% 
      st_cast("POLYGON") %>%
      st_convex_hull() %>% 
      st_transform(4326)
  } else {
    data %>%
      st_cast("POLYGON") %>%
      st_convex_hull() %>% 
      st_transform(4326)
  }
}

## For some reason sf package does not let me have poygons made from point buffers be in the same df that contains regular polygons, so we split them: 

PaTi_polygon_pl <- PaTi_polygon_1 %>%
  rbind(PaTi_polygon_2) %>%
  filter(n_link > 1) %>% 
  PaTi_polygon_make()

PaTi_polygon_pt <- PaTi_polygon_1 %>%
  rbind(PaTi_polygon_2) %>%
  filter(n_link == 1) %>% 
  PaTi_polygon_make()
  

# leaf_sf(tt[1,] %>% st_transform(4326)) %>% 
#   addPolygons(data = tt2[1,],
#               popup=paste("Stratum:",tt[1,]$infraction_code,"<br>"),
#               label = ~ paste0("Total Income: ", infraction_code))
# 
# leaflet() %>% 
#   addProviderTiles(
#     "OpenStreetMap",
#     # give the layer a name
#     group = "OpenStreetMap"
#   ) %>% 
#   addPolygons(data = tt2[1,],
#               popup=paste("Stratum:",tt[1,]$infraction_code,"<br>"),
#               label = ~ paste0("Total Income: ", infraction_code))
pal <- colorBin(colorRampPalette(c("#d0073a","#000000"))(20),
                domain = PaTi_polygon_pl$no_infraction)

leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(data = PaTi_polygon_pl,
              popup=paste(#"<b>Infraction Code</b>",PaTi_polygon_pl$infraction_code,"<br>",
                          "<b>Description:</b>",PaTi_polygon_pl$infraction_description,"<br>",
                          "<b>Location:</b>",PaTi_polygon_pl$LFNAME,"<br>",
                          "<b>Number of Infraction:</b>",PaTi_polygon_pl$no_infraction,"<br>"),
              label = ~ paste0("Infraction Code ", infraction_code),
              color = #colorRampPalette(c("#d0073a","#000000")))
                ~ pal(no_infraction)) %>% 
  addPolygons(data = PaTi_polygon_pt,
              popup=paste("Stratum:",PaTi_polygon_pt$infraction_code,"<br>",
                          "<b>Location:</b>",PaTi_polygon_pl$LFNAME,"<br>",
                          "Description:",PaTi_polygon_pl$infraction_description),
              label = ~ paste0("Infraction Code ", infraction_code),
              color = ~ pal(no_infraction)) %>% 
  addLegend(
    data = PaTi_polygon_pl,
    pal = pal,
    values = ~no_infraction,
    position = "bottomleft",
    title = "Number of Infraction:",
    opacity = 1
  )
```


```{r Green P API}
GeoC_metadata <- opendatatoronto::show_package("https://open.toronto.ca/dataset/address-points-municipal-toronto-one-address-repository/")
GeoC_list <- opendatatoronto::list_package_resources("https://open.toronto.ca/dataset/address-points-municipal-toronto-one-address-repository/")
GeoC_retrieve <- function() {
  GeoC_data_id <- GeoC_list[[3, "id"]]
  resource <-
    resource_show(GeoC_data_id, url = "https://ckan0.cf.opendata.inter.prod-toronto.ca/", as = "list")
  dir <- tempdir()
  resource_dir <- fs::dir_create(paste0(dir, "/", GeoC_data_id))
  save_path <-
    ckan_fetch(
      resource[["url"]],
      store = "disk",
      path = paste0(dir, "/", GeoC_data_id, "/", "res.zip")
    )
  GeoC_files <- unzip(save_path[["path"]], exdir = resource_dir)
  GeoC_shp <- st_read(GeoC_files[str_ends(GeoC_files, ".shp")])
}

GeoC_shp <- GeoC_retrieve()
```


```{r}
PaTi_data_top20_2tt <- PaTi_data_top20_split[!PaTi_data_top20_split$group,] %>%  
  group_by(infraction_code,location2,location4) %>% 
  summarise(n=n()) %>% 
  rowwise() %>%
  mutate(location2 = tolower(str_trim(location2)),
         location4 = tolower(str_trim(location4))) 

PaTi_data_top20_2tt %>% arrange(desc(n))

st_as_sf(as.data.frame(tt3[c(1,1,2,3),]),coords = c("X","Y")) %>% summarise()
st_sf
st_as
  PaTi_polygon_make()

PaTi_polygon %>% 
  filter(n_link == 1) %>% 
  st_transform(3347) %>% 
  st_buffer(dist = 10) %>% 
  st_transform(4326)


  
PaTi_polygon %>% st_transform(3347)

PaTi_polygon <- GeoC_shp %>% 
  filter(LINK %in% PaTi_data_top20[PaTi_data_top20$reference_type == "LINK",]$reference) %>% 
  rbind(GeoC_shp %>% filter(GEO_ID %in% PaTi_data_top20[PaTi_data_top20$reference_type == "GEO_ID",]$reference)) %>%
  group_by(LINK) %>% 
  summarise() %>%
  st_cast("MULTIPOINT") %>% 
  st_cast("POLYGON") %>% 
  st_convex_hull()
  


tt <- GeoC_shp %>% 
  filter(LINK %in% PaTi_data_top20[PaTi_data_top20$reference_type == "LINK",]$reference) %>% 
  rbind(GeoC_shp %>% filter(GEO_ID %in% PaTi_data_top20[PaTi_data_top20$reference_type == "GEO_ID",]$reference)) %>% 
  group_by(LINK) %>% 
  mutate(n_link=n()) %>% 
  filter(n_link>3) %>% 
  summarise() %>%
  # st_cast("MULTIPOINT") %>% 
  st_cast("POLYGON") %>% 
  st_convex_hull()

PaTi_polygon[1,] %>% 
  st_cast("POLYGON") %>% 
  st_convex_hull()
  
  
plot(tt)


library(leaflet)
install.packages("simplevis")
library(simplevis)
leaf_sf_col(tt %>% st_transform(4326))
simplevis::l

leaf_sf(tt %>% st_transform(4326))


leaflet(tt %>% st_transform(4326)) %>% 
  # addProviderTiles("CartoDB.Positron") %>% 
  addPolygons(color = "green")
leaflet::leaflet(tt) %>% leaflet::addPolygons(tt)

m <- leaflet() %>%
   addTiles()
m



tt %>% st_transform(4326)

GeoC_shp %>% 
  filter(LINK %in% PaTi_data_top20[PaTi_data_top20$reference_type == "LINK",]$reference) %>% 
  rbind(GeoC_shp %>% filter(GEO_ID %in% PaTi_data_top20[PaTi_data_top20$reference_type == "GEO_ID",]$reference)) %>% 
  group_by(LINK) %>% 
  summarise(n_link=n())


tt2 <- GeoC_shp[c(1,1,1,1),] %>% 
  group_by(LINK) %>% 
  summarise() %>%
  st_cast("MULTIPOINT") %>% 
  st_cast("POLYGON")

tt3 <- GeoC_shp %>% filter(LINK == 30034748	)
tt3 <- tt3[c(1,1,2,3),]
tt3 %>% 
  group_by(LINK) %>% 
  summarise() %>%
  st_cast("MULTIPOINT") %>% 
  st_cast("POLYGON")


rep(GeoC_shp[1,])

GeoC_shp %>% st_drop_geometry() %>% filter(GEO_ID == 14200303)

14670981 %in% PaTi_data_top20$reference

```


```{r}
grepl('^\\d', "1ABC")
grepl('^[[:punct:]]?\\d', "#16")
str_extract(str_extract("#16A Ahwaz","^[:punct:]?\\d*((?<=\\d)[:alpha:](?=\\s))?"),"[^[:punct:]]+")
str_extract(str_extract(location2,"^[:punct:]?\\d*((?<=\\d)[:alpha:](?=\\s))?"),"[^[:punct:]]+")

str_extract("#2","(?<=[:punct:])\\d?")
  left_join((GeoC_shp %>% select(GEO_ID,LINK,LFNAME_lower,ADDRESS)),by = c("LFNAME_lower","ADDRESS")) %>% 
  group_by(infraction_code, LINK) %>%
  summarise(n = sum(n,na.rm = TRUE)) %>% 
  mutate(accurate_type = T)



GeoC_shp %>% filter(LFNAME == "Lake Promenade")
GeoC_shp %>% mutate(row_num = row_number()) %>% filter(str_like(LFNAME_lower,"clendenan ave"),ADDRESS == 573)
PaTi_data_tot[1,] %>% separate(location2,into = c("ADDRESS","LFNAME"),sep = "(?<=[0-9])(?=\\s?[A-Z])",remove = FALSE)

PaTi_data_tot %>% filter(infraction_code == 134)
PaTi_data_tot %>% filter(!is.na(location2),!is.na(location4))
```


```{r}
PaTi_data_tot[1:100,] %>%
  group_by(infraction_code,location2) %>% 
  summarise(n=n()) %>% 
  rowwise() %>%
  mutate(ADDRESS = str_extract(location2,"^\\d*((?<=\\d)[:alpha:])?"),
         LFNAME_lower = tolower(str_trim(sub(ADDRESS,"",location2)))) %>% 
  left_join((GeoC_shp %>% select(GEO_ID,LINK,LFNAME_lower,ADDRESS)),by = c("LFNAME_lower","ADDRESS")) %>%
  group_by(infraction_code, LINK) %>%
  summarise(n = sum(n,na.rm = TRUE))

tt1 <- PaTi_data_tot[1:100,] %>%
  rowwise() %>%
  mutate(ADDRESS = str_extract(location2,"^\\d*((?<=\\d)[:alpha:])?"),
         LFNAME_lower = tolower(str_trim(sub(ADDRESS,"",location2))))
  separate(location2,into = c("ADDRESS","LFNAME"),sep = "(?<=[0-9])(?=\\s?[a-zA-Z])",remove = FALSE) %>%
  mutate(LFNAME = tolower(LFNAME))

  
tt2 <- PaTi_data_tot[1:100,] %>%
  rowwise() %>%
  # group_by(infraction_code,location2) %>% 
  # summarise(n=n()) %>% 
  mutate(ADDRESS = str_extract(location2,"^\\d*((?<=\\d)[:alpha:])?"),
         LFNAME_lower = tolower(str_trim(sub(ADDRESS,"",location2))))

         LFNAME_lower = tolower(str_extract(location2,"\\D*$")))
  
tt2 <- PaTi_data_tot[1:100,]
tt2$location2[1] = "16A Ahwaz"
tt2 %>% rowwise() %>% 
  # group_by(infraction_code,location2) %>% 
  # summarise(n=n()) %>% 
  mutate(ADDRESS = str_extract(location2,"^\\d*(\\d[:alpha:])?"),
         LFNAME = str_trim(sub(ADDRESS,"",location2)))

str_extract("16A Ahwaz","^\\d*((?<=\\d)[:alpha:])?")
str_extract("16A Ahwaz","(?<=\\d)[:alpha:]")

GeoC_shp %>% st_drop_geometry() %>% filter(LFNAME_lower == "harrison st")
str_sub()
sub("573","","573 CLENDENAN AVE")
sepa
sub("k","","kjnas")
"kjnas" - "k"

```
```{r}
GeoC_shp %>% st_drop_geometry() %>% filter(LFNAME_lower == tolower("HARRISON ST")) %>% inner_join((GeoC_shp %>% st_drop_geometry() %>% filter(LFNAME_lower == tolower("SHAW ST"))),by = "LINK")

tt3 <- GeoC_shp %>% st_drop_geometry() %>% filter(LFNAME_lower == tolower("HARRISON ST"))
tt4 <- GeoC_shp %>% st_drop_geometry() %>% filter(LFNAME_lower == tolower("SHAW ST"))
tt3$LINK %in% tt4$LINK

GeoC_shp %>% st_drop_geometry() %>% filter(LFNAME_lower == tolower("SHAW ST"),ADDRESS == "336")
GeoC_shp %>% st_drop_geometry() %>% filter(LINK == 30096117) %>% arrange(ADDRESS)


tt3 <- GeoC_shp %>% st_drop_geometry() %>% filter(LFNAME_lower == tolower("SHERBOURNE ST"))
tt4 <- GeoC_shp %>% st_drop_geometry() %>% filter(LFNAME_lower == tolower("GERRARD ST E"))
any(tt3$LINK %in% tt4$LINK)
any(tt3$FCODE %in% tt4$FCODE)

unique((GeoC_shp %>% st_drop_geometry())$FCODE)

tt3 %>% select(-MAINT_STAG,-ADDRESS,-LO_NUM,-LONUMSUF,HINUM,HINUMSUF,ARC_SIDE,-DISTANCE,-FCODE_DES,-CLASS,-MUN_NAME,-WARD_NAME-)

GeoC_shp %>% st_drop_geometry() %>% filter(LFNAME_lower == tolower("SHAW ST"),ADDRESS == "440")
GeoC_shp %>% st_drop_geometry() %>% filter(LINK == 14019718) %>% arrange(ADDRESS)

GeoC_shp %>% st_drop_geometry() %>% filter(LFNAME_lower == tolower("COLLEGE ST"),ADDRESS == "795")
GeoC_shp %>% st_drop_geometry() %>% filter(LINK == 1144747) %>% arrange(ADDRESS)

GeoC_shp %>% st_drop_geometry() %>% filter(LINK == 14019718) %>% arrange(OBJECTID)
GeoC_shp %>% st_drop_geometry() %>% filter(LINK == 1144747) %>% arrange(DISTANCE)

GeoC_shp %>% st_drop_geometry() %>% group_by(LINK) %>% summarise(n=n()) %>% arrange(desc(n))
GeoC_shp %>% st_drop_geometry() %>% filter(LINK == 30081011) %>% arrange(ADDRESS)
2057097
2232038

785502
acores ave

GeoC_shp %>% st_drop_geometry() %>% filter(LFNAME_lower == tolower("SHAW ST")) %>% group_by(LINK)
GeoC_shp %>% filter(LFNAME_lower == tolower("SHAW ST")) %>% group_by(LINK) %>% filter(DISTANCE %in% c(min(DISTANCE),max(DISTANCE))) %>% arrange(LINK,DISTANCE) %>% mutate(n=n()) %>% filter(n<2)

GeoC_shp %>% st_drop_geometry() %>% filter(LFNAME_lower == tolower("plante ave"))
GeoC_shp %>% st_drop_geometry() %>% filter(str_like(LFNAME_lower,tolower("st luke lane")))
GeoC_shp %>% st_drop_geometry() %>% filter(LINK == 30070016) %>% arrange(DISTANCE)
GeoC_shp %>% st_drop_geometry() %>% filter(LINK == 14621076) %>% arrange(DISTANCE)
```
```{r}
shp1 <- GeoC_shp %>% 
    filter(LFNAME_lower == tolower("HARRISON ST")) %>%
    group_by(LINK) %>% 
    filter(DISTANCE %in% c(min(DISTANCE),max(DISTANCE)))
  
  shp2 <- GeoC_shp %>% 
    filter(LFNAME_lower == tolower("SHAW ST")) %>%
    group_by(LINK) %>% 
    filter(DISTANCE %in% c(min(DISTANCE),max(DISTANCE)))
  
min(st_distance(shp1,shp2))

tt8 <- st_distance(shp1,shp2)
as.array(tt8)
which(tt8 == min(tt8), arr.ind = TRUE)
```


```{r API Query}
parking_packages <- search_packages("parking")

P_ticket <- httr::GET("https://open.toronto.ca/dataset/parking-tickets/")
P_ticket
```



```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
